---
title: "ggplot_hook"
author: "David Sabalete"
date: "2023-05-18"
output:
  html_document: default
  pdf_document: default
---

## Setting up my environment
Notes: setting up my R environment by loading the 'tidyverse' and 'palmerpenguins' packages

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
library(tinytex)
```

## Visualizations
Here we will go through a series of visualizations

### Flipper and body mass in purple
Here, we plot flipper length against body mass

```{r visualize flipper and body mass in purple}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(color="purple")
```

### Flipper and obdy mass by species
Here, we plot flipper length against body mass and look at the breakdown by species

```{r species}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(aes(shape=species))
```



### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by species and sex

```{r visualize flipper and body mass separated by species}
penguins %>% 
  drop_na(sex) %>% 
  ggplot(aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(aes(color=species, shape=species)) +
  facet_wrap(~sex)
```

```{r get a glimpse of penguins data frame}
glimpse(penguins)
```